Functional oxide layers for electrical isolation and chemical passivation of steel substrates

### 2022-05-17 Thesis/chapter/03-theoretical-background.tex
IR freewriting of chapter from schwedt

\subsubsection{Infrared absorption}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47
}
\subsubsection{X-Ray Diffraction}
\gls{xrd} is used to study the crystalline strucutre of materlias since X-rays wavelengths (between 0.2 and \nm{10}) are comparable to the interatomic spacing of crystalline solids.  \cite{Kaliva2020}.
Each crystalline material has discreet atomc structure, which upon irradiation with X-rays causes constructive and destructive interference and generates unique diffraction patterns. 
XRD \td{spectra} of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad cruve with a maximum extending over several degrees (2$\theta$).

>>>>

\subsubsection{Infrared absorption}
\td{IR around page 45;
REFLECTIVITY? can also be used for determination of thickness p47
}
\td{what, how, why?}
\Gls{ir} spectroscopy is molecular spectroscopic method using interactions of \gls{ir} light (wavelengths $\lambda$ of between $10^{-3}$ and $10^{-6}$ \nm{}) with molecules. \cite{Schwedt2008}
\td{FREE WRITING:}
light is described as periodic electro magnetic wave which moves. 
All \gls{em} waves move with the speed of light c = 300k km /s in vacuum. 
talk about $E=h\cdot v$ and $\nu=c/\lambda$ and $\bar{\nu}=1/\lambda$
shorter wavelengths (higher frequencies) carry more energy. 
In practice the spectrum \gls{em} waves are unterteilt in different things. 
from high to low energie: Xray, \gls{uv}, vis, (near, middle and far) \gls{ir}, microwaves and radiowaves. 
Xrays interact with core electrons, \gls{uv} and vis with valence electrons, ir with schwingungne mol rot and translation, microwaves with rotation and radio with electron and nuclear spin. 
molecular vibrations are unterteilt in valenz and deformation vibration.
absorbance pre din 1349: $A(\lambda) = \log{\frac{\phi_{in}}{\phi_{ex}}}$ and transmission $\tau =T=D= \phi_{ex}/\phi_{in}$
The absorbance intensity is abhaengig von wave length and molecule structure. 
Frank-Condon rules, spin verbot and symmetrie verbot are ausschlaggebend für the resulting spectrum.

Ein molekule hat $F=3N$ (N anzahl der atome) freiheitsgrade, wobei $F_T=3$ translation und $F_R=3$ (2 für lineare molecules) wodurch sich die anzahl der vibration reduces to $F_V=3N-6$ ($3N-5$) for vibrations. 
vibrations are unterteils in valence vibrations (change of bond length) and deformation (change of bindungs angle). 
only vibrations with change in dipole momemnt are \gls{ir} active.

differences to UVVis: transmission instead of absorbance, higher energy left instead right, base line on top instead of bottom.
\paragraph{(Fourier Transform) Infrared spectrometer}
 A ceramic material (Nernst glower) is heated to \oc{1600} as light source. 
 In the two strahlen spectrometer the light is split, send through the sample and a reference, combined and send through a monochromator to a detector. 
 In the \gls{ft}\gls{ir} spectrometer the beam is send thourhg the sample, split and reflected from a static and from a moving mirror, recombined and detected by a photo multiplier (a bauteil which transforms photons into electircal signals).

\subsubsection{X-Ray Diffraction}
\gls{xrd} is used to study the crystalline strucutre of materlias since X-rays wavelengths (between 0.2 and \nm{10}) are comparable to the interatomic spacing of crystalline solids.  \cite{Kaliva2020}.
Each crystalline material has discreet atomc structure, which upon irradiation with X-rays causes constructive and destructive interference and generates unique diffraction patterns. 
XRD \td{spectra} of crystalline materials feature distinct peaks, whereas amorphous materials exhibit a broad cruve with a maximum extending over several degrees (2$\theta$).
